Windowed least-squares model reduction for dynamical systems

### 2019-10-14 section4/numerical_methods.tex
thru 3

\section{Numerical solution techniques}\label{sec:numerical_techniques}
The discussion to this point has outlined the formulation of the \methodAcronym\ method. We now consider numerical solution techniques. 
\methodAcronym\ displays commonalities with optimal
control problems, and as such a large existing body of work can be leveraged. In this section we 
outline a variety of such techniques. We focus primarily on 
%\KTC{earlier we kept
%saying 
%direct (i.e.,
%	discretize-then-optimize) and indirect (i.e., optimize-then-discretize).
%	Let's be consistent when we re-introduce it here.}
direct (discretize-the-optimize) and indirect (optimize-then-discretize) for \spatialAcronym\ trial subspaces, 
and then briefly outline direct and indirect methods for \spaceTimeAcronym\ trial subspaces.

>>>>

\section{Numerical solution techniques}\label{sec:numerical_techniques}
\KTC{HERE}
The discussion to this point has outlined the formulation of the \methodAcronym\ method. We now consider numerical solution techniques. 
\methodAcronym\ displays commonalities with optimal
control problems, and as such a large existing body of work can be leveraged. In this section we 
outline a variety of such techniques. We focus primarily on 
%\KTC{earlier we kept
%saying 
%direct (i.e.,
%	discretize-then-optimize) and indirect (i.e., optimize-then-discretize).
%	Let's be consistent when we re-introduce it here.}
direct (discretize-the-optimize) and indirect (optimize-then-discretize) for \spatialAcronym\ trial subspaces, 
and then briefly outline direct and indirect methods for \spaceTimeAcronym\ trial subspaces.
